Geometric variational problems

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
Update broaderimpacts.tex

\section{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with 
less computational cost than molecular dynamics, and account for more general
features that continuum theory misses. The main ingredient is defining a 
nonlocal interaction through the solution of an elliptic boundary value problem
that has the phenomenological characteristics of long-range hydrophobic
attraction. It turns out that this minimal model gives rise to rich phenomena
for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
The technical research tasks includes quantifying collective properties of 
amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
efficient, high-order numerical algorithms for large-scale simulations, and 
incorporating external fields such as electric charge. Lastly, the proposal 
extends the results using three-dimensional boundary integral formulations.

>>>>

\section{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with 
less computational cost than molecular dynamics, and account for more general
features that continuum theory misses. The main ingredient is defining a 
nonlocal interaction through the solution of an elliptic boundary value problem
that has the phenomenological characteristics of long-range hydrophobic
attraction. It turns out that this minimal model gives rise to rich phenomena
for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
The technical research tasks include quantifying collective properties of 
amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
efficient, high-order numerical algorithms for large-scale simulations, and 
incorporating external fields such as through electric charge. Lastly, the proposal 
extends the results using three-dimensional boundary integral formulations.
